Notes on area-length problem for CLE

### 2013-12-14 area-length/notes.tex
Minor changes

Though several publications exist
\cite{cardy2003exact,cardy2003crossover,cardy2001exact,cardy1994geometrical}
on this problem and the answer is
obtained from computer simulation \cite{richard2001scaling}, good understanding was not
obtained.

@@

Partition function for $O(n)$ model is
\begin{equation}
  \label{eq:9}
  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
  n^{\mbox{number of loops}}
\end{equation}
Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
limit in this point is described by minimal model $(p,p')$ with
$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=$.

@@

@@

@@

Here
\begin{equation}
  \label{eq:8}
  Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
  \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
\end{equation}

@@

@@

Since our four-point function satisfy second order ODE, it can be presented as a linear combination
of two independent solutions -- conformal blocks. Change of variables allows to rewrite the equation
as a hypergeometric equation, so conformal blocks are given by hypergeometric functions:
\begin{equation}
  \label{eq:71}
  \mathcal{G}_{\pm}(x,z)=\frac{|x-\bar x|^{2\Delta_{\alpha}-2\Delta_{-\frac{b}{2}}}}{|z-\bar
    x|^{4\Delta_{\alpha}}} \mathcal{F}_{\pm}(\eta),
\end{equation}
where $\Delta_{-\frac{b}{2}}=-\frac{1}{2}-\frac{3b^{2}}{4}$ and 
\begin{equation}
  \label{eq:72}
  \eta=\frac{(z-x)(\bar z-\bar x)}{(z-\bar x)(\bar z - x)}
\end{equation}
\begin{eqnarray}
  \label{eq:73}
  F_{+}(\eta)=\eta^{\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(2\alpha b -1-2b^{2},-b^{2},2\alpha
  b-b^{2};\eta)\\
  F_{-}(\eta)=\eta^{1+b^{2}-\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(-b^{2},1-2\alpha b,2+b^{2}-2\alpha
  b;\eta)
\end{eqnarray}
Coefficients before independent solutions $\mathcal{G}_{\pm}$ are fixed by substituting OPE
\eqref{eq:35}:
\begin{equation}
  \label{eq:74}
  G_{\alpha,-\frac{b}{2}}=C_{+}(\alpha) U\left(\alpha-\frac{b}{2}\right) \mathcal{G}_{+}(x,z)+
  C_{-}(\alpha) U\left(\alpha+\frac{b}{2}\right) \mathcal{G}_{-}(x,z)
\end{equation}
Next we need to consider OPE when both operators $V_{\alpha}(x), V_{-\frac{b}{2}}(z)$ approach the
boundary. 
\section{Scaling limit and CFT on a cone}
\label{sec:scaling-limit-cft}

>>>>

Though several publications exist
\cite{cardy2003exact,cardy2003crossover,cardy2001exact,cardy1994geometrical}
on this problem and the answer is
obtained from computer simulation \cite{ richard2001scaling}, good understanding was not
obtained.

\subsection{Self-avoiding polygons}
\label{sec:self-avoid-polyg}

The model of self-avoiding polygons was numerically studied in the paper \cite{richard2001scaling}.
Author consider polygons with generating function
\begin{equation}
  \label{eq:75}
  G(x,q)=\sum_{m,n} p_{m,n} x^{m} q^{n},
\end{equation}
where $p_{m,n}$ is the number of polygons with perimeter $m$, enclosing an area $n$ passing through
a given edge (or node). 
Cardy \cite{cardy2001exact} use following definition for generating function of rooted loops, using
$g=-\ln q$:
\begin{equation}
  \label{eq:76}
  G^{(r)}(x,g)=\sum_{l,A} p_{l,A}^{(r)} x^{l} e^{-gA}
\end{equation}
Generating function for rooted polygons $G^{(r)}(x,g)$ is related to $G(x,g)$ by
\begin{equation}
  \label{eq:81}
  G^{(r)}(x,g)=x \frac{d}{dx} G(x,g),
\end{equation}
because root can be chosen in $l$ ways.

This model has critical point $(x_{c},0)$ and generating functions displays scaling behavior
\begin{equation}
  \label{eq:77}
  G(x,g)\sim G(x,g)_{\mathrm{reg}}+g^{\theta} F\left((x_{c}-x)g^{-\phi}\right)
\end{equation}
Critical indices $\theta,\phi$ are related to conventional exponents $\nu,\alpha$:
\begin{eqnarray}
  \label{eq:78}
  \phi=\frac{1}{2}\nu\\
  \theta=\frac{1}{2}(1-\alpha) \nu
\end{eqnarray}
Hyperscaling hypothesis adds another relation
\begin{equation}
  \label{eq:79}
  \alpha=2-2\nu
\end{equation}
Numerical results predict
\begin{eqnarray}
  \label{eq:80}
  \nu=\frac{3}{4}\\
  \theta=\frac{1}{3}\\
  \phi=\frac{2}{3}
\end{eqnarray}
We want to find scaling function $F$.

@@

Self-avoiding polygons can be thought as the limit $n\to 0$ of loops in $O(n)$ model.

Partition function for $O(n)$ model is
\begin{equation}
  \label{eq:9}
  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
  n^{\mbox{number of loops}}
\end{equation}
Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
limit in this point is described by minimal model $(p,p')$ with
$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=\sqrt{\frac{3}{2}}$.

@@

Logarithmic CFT $\sim$ Liouville theory ???

@@

Cardy \cite{cardy2001exact} argues that generating function $G^{(r)}$ for rooted self-avoiding loops is given by a derivative w.r.t. $x$
of expectation value of $e^{-gA}$ (eq.6):
\begin{equation}
  \label{eq:82}
  Z=\left<e^{-gA}\right>_{\mathrm{SAL}}=\left<e^{-\sqrt{g}\int J_{\lambda}A_{\lambda}d^{2}x}\right>_{\mathrm{SAL}.A}
\end{equation}
But reasoning is quite strange and unsound.

@@

Here
\begin{equation}
  \label{eq:8}
  Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
  \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
\end{equation}
 Very strange.

@@

Liouville theory describes internal metric of surface. It is possible to obtain length of boundary
and area of surface with such a metric. To get the answer for flat loops we need to impose some
condition on metric in the bulk. 
It is
\begin{equation}
  \label{eq:83}
  g^{ab}=\eta^{ab}
\end{equation}
where
\begin{equation}
  \label{eq:84}
  g^{ab}=e^{2b\varphi} \eta^{ab}
\end{equation}
So the condition is
\begin{equation}
  \label{eq:85}
  \varphi(x) = 0 
\end{equation}

@@

Since our four-point function satisfy second order ODE, it can be presented as a linear combination
of two independent solutions -- conformal blocks. Change of variables allows to rewrite the equation
as a hypergeometric equation, so conformal blocks are given by hypergeometric functions:
\begin{equation}
  \label{eq:71}
  \mathcal{G}_{\pm}(x,z)=\frac{|x-\bar x|^{2\Delta_{\alpha}-2\Delta_{-\frac{b}{2}}}}{|z-\bar
    x|^{4\Delta_{\alpha}}} \mathcal{F}_{\pm}(\eta),
\end{equation}
where $\Delta_{-\frac{b}{2}}=-\frac{1}{2}-\frac{3b^{2}}{4}$ and 
\begin{equation}
  \label{eq:72}
  \eta=\frac{(z-x)(\bar z-\bar x)}{(z-\bar x)(\bar z - x)}
\end{equation}
\begin{eqnarray}
  \label{eq:73}
  F_{+}(\eta)=\eta^{\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(2\alpha b -1-2b^{2},-b^{2},2\alpha
  b-b^{2};\eta)\\
  F_{-}(\eta)=\eta^{1+b^{2}-\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(-b^{2},1-2\alpha b,2+b^{2}-2\alpha
  b;\eta)
\end{eqnarray}
Coefficients before independent solutions $\mathcal{G}_{\pm}$ are fixed by substituting OPE
\eqref{eq:35} (substitute it to equation?):
\begin{equation}
  \label{eq:74}
  G_{\alpha,-\frac{b}{2}}=C_{+}(\alpha) U\left(\alpha-\frac{b}{2}\right) \mathcal{G}_{+}(x,z)+
  C_{-}(\alpha) U\left(\alpha+\frac{b}{2}\right) \mathcal{G}_{-}(x,z)
\end{equation}
Next we need to consider OPE when both operators $V_{\alpha}(x), V_{-\frac{b}{2}}(z)$ approach the
boundary.

Bulk operator $V_{-\frac{b}{2}}$ near the boundary gives rise to two boundary families $B_{0}$ and
$B_{-b}$. The fusion of $B_{0}=I$ to $V_{\alpha}$ is $\left<V_{\alpha}(x)
  B_{0}(0)\right>=\frac{R(\alpha,0|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}$, and the fusion of $V_{-\frac{b}{2}}$ 
\section{Scaling limit and CFT on a cone}
\label{sec:scaling-limit-cft}
